---
title: "Laboratory Efficiency Indicators: 30 Day Lookback"
date: "7/24/2020"
output: html_document
---

<h2><span style="color: red;">Draft - Not for Distribution</span></h2>


```{r Install and load packages, echo = FALSE, warning = FALSE, message = FALSE}
#Install packages only the first time you run the code
#install.packages("timeDate")
#install.packages("lubridate")
#install.packages("readxl")
#install.packages("writexl")
#install.packages("dplyr")
#install.packages("reshape2")
#install.packages("knitr")
#install.packages("kableExtra")
#install.packages("formattable")
#install.packages("bizdays")
#install.packages("rmarkdown")
#install.packages("stringr")
#install.packages("tinytex")
#install.packages("scales")
#install.packages("gridExtra")
#install.packages("ggQC")


#-------------------------------Required packages-------------------------------#

#Required packages: run these everytime you run the code
library(timeDate)
library(readxl)
library(bizdays)
library(dplyr)
library(lubridate)
library(reshape2)
library(knitr)
library(kableExtra)
library(formattable)
library(rmarkdown)
library(stringr)
library(writexl)
library(ggplot2)
library(gridExtra)
library(scales)
library(ggQC)
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r Clear history and import relevant data, echo = FALSE, warning = FALSE, message = FALSE}
rm(list = ls())

user_wd <- "J:\\Deans\\Presidents\\HSPI-PM\\Operations Analytics and Optimization\\Projects\\Service Lines\\Lab KPI\\Data"
cp_user_path <- paste0(user_wd, "\\SCC Sunquest Script Repo\\*.*")
ap_user_path <- paste0(user_wd, "\\AP & Cytology Historical Repo\\*.*")
setwd(user_wd)

# Import Clinical Pathology historical repository (Sunquest and SCC)
scc_sun_hist <- read_excel(choose.files(default = cp_user_path, caption = "Select Historical Repository"), sheet = 1, col_names = TRUE)

# Import Anatomic Pathology historica repository (PowerPath)
AP_historical_repo <- read_excel(choose.files(default = ap_user_path, caption = "Select Anatomic Pathology Historical Repository"), sheet=1,  col_names = TRUE)

# Determine start date based on lookback period and last date in repository
scc_sun_hist$ResultDate <- as.Date(scc_sun_hist$ResultDate, format = "%m/%d/%y")
lookback_period <- 30
start_date <- max(scc_sun_hist$ResultDate) - (lookback_period - 1)

# Orders for labs, sites, patient setting, and priority
cp_micro_lab_order <- c("Troponin", "Lactate WB", "BUN", "HGB", "PT", "Rapid Flu", "C. diff")
site_order <- c("MSH", "MSQ", "MSBI", "MSB", "MSW", "MSM")
dashboard_pt_setting <- c("ED & ICU", "IP Non-ICU", "Amb")
dashboard_priority_order <- c("All", "Stat", "Routine")

#user_wd <- "J:\\deans\\Presidents\\HSPI-PM\\Operations Analytics and Optimization\\Projects\\Service Lines\\Lab KPI\\Data\\AP & Cytology Historical Repo"
#user_path <- paste0(user_wd, "\\*.*")

# Sinai color scheme
mshs_colors = c("#221f72", "#00AEFF", "#D80B8C", "#7f7f7f")
```

```{r Format historical repository for Clinical Pathology plotting, echo = FALSE, warning = FALSE, message = FALSE}
cp_dashboard_tat_summary <- scc_sun_hist %>%
  group_by(Site, ResultDate, Division, Test, 
           DashboardPriority, DashboardSetting, 
           ReceiveResultTarget, CollectResultTarget) %>%
  summarize(ResultedVolume = sum(TotalResulted), 
            ResultedVolumeWithTAT = sum(TotalResultedTAT), 
            ReceiveResultInTarget = sum(TotalReceiveResultInTarget), 
            CollectResultInTarget = sum(TotalCollectResultInTarget)) %>%
  mutate(ReceiveResultDefects = ResultedVolumeWithTAT - ReceiveResultInTarget,
         CollectResultDefects = ResultedVolumeWithTAT - CollectResultInTarget,
         ReceiveResultPercent = ReceiveResultInTarget / ResultedVolumeWithTAT,
         CollectResultPercent = CollectResultInTarget / ResultedVolumeWithTAT,
         SafeThreshold = ifelse(Test == "Rapid Flu" | Test == "C. diff", 1.0, 0.95),
         NotSafeThreshold = ifelse(Test == "Rapid Flu" | Test == "C. diff", 0.9, 0.8))

cp_dashboard_vol_summary <- scc_sun_hist %>%
  group_by(Site, ResultDate, Test, DashboardPriority) %>%
  summarize(ResultedVolume = sum(TotalResulted))

```

```{r Filter unused TAT combinations for Clinical Pathology, echo = FALSE, warning = FALSE, message = FALSE}
# Manually remove patient settings or combinations not represented in efficiency indicator dashboards
cp_dashboard_tat_filter <- cp_dashboard_tat_summary %>%
  filter(!(DashboardPriority == "Other" | DashboardSetting == "Other" | 
             ((Test == "Troponin" | Test == "Lactate WB") & DashboardSetting == "Amb") |
             (Test == "C. diff" & DashboardSetting == "Amb")))

# Convert characters to factors
cp_dashboard_tat_filter$Site <- factor(cp_dashboard_tat_filter$Site, levels = site_order)
cp_dashboard_tat_filter$Test <- factor(cp_dashboard_tat_filter$Test, levels = cp_micro_lab_order)
cp_dashboard_tat_filter$DashboardPriority <- factor(cp_dashboard_tat_filter$DashboardPriority, levels = dashboard_priority_order)
cp_dashboard_tat_filter$DashboardSetting <- factor(cp_dashboard_tat_filter$DashboardSetting, levels = dashboard_pt_setting)

# Sort data frame
cp_dashboard_tat_filter <- cp_dashboard_tat_filter %>%
  arrange(Test, Site, DashboardPriority, DashboardSetting, ResultDate)

```

```{r Custom function for graphing TAT percentage for Clinical Pathology, echo = FALSE, warning = FALSE, message = FALSE}
cp_tat_percentage_graph <- function(data, test_name, site_name, lab_priority, metric) {
  metric_name <- ifelse(metric == "ReceiveResultPercent", "Receive to Result TAT", ifelse(metric == "CollectResultPercent", "Collect to Result TAT", "Error"))
  # df <- data[data$ResultDate >= start_date & data$Test == test & data$Site == site & data$DashboardPriority == lab_priority, ]
  # 
  ggplot() +
    geom_rect(aes(xmin = start_date - 1, xmax = max(data$ResultDate) + 1, ymin = -Inf, ymax = min(data$NotSafeThreshold), fill = "Not Safe", alpha = "Not Safe")) +
    geom_rect(aes(xmin = start_date - 1, xmax = max(data$ResultDate) + 1, ymin = min(data$NotSafeThreshold), ymax = min(data$SafeThreshold), fill = "At Risk", alpha = "At Risk")) +
    geom_rect(aes(xmin = start_date - 1, xmax = max(data$ResultDate) + 1, ymin = min(data$SafeThreshold), ymax = Inf, fill = "Safe", alpha = "Safe")) +
    geom_point(data = data[data$ResultDate >= start_date & data$Test == test_name & data$Site == site_name & data$DashboardPriority == lab_priority, ], aes_string(x = "ResultDate", y = metric, color = "DashboardSetting", shape = "DashboardSetting"), size = 3) +
    geom_line(data = data[data$ResultDate >= start_date & data$Test == test_name & data$Site == site_name & data$DashboardPriority == lab_priority, ], aes_string(x = "ResultDate", y = metric, color = "DashboardSetting"), linetype = "dashed") +
    labs(title = paste0(test_name, " ", metric_name, ":\n", site_name, " Percentage of ", lab_priority, " Labs within Target"), x = "Date",  y = "Percentage of Labs", color = "Setting", shape = "Setting") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "right", legend.box = "vertical", legend.title = element_text(size = 10), legend.text = element_text(size = 8),axis.text.x = element_text(angle = 30, hjust = 1)) +
    scale_x_date(limits = c(start_date -1, max(data$ResultDate)+1), breaks = seq(start_date, max(data$ResultDate), by = 3), date_minor_breaks = "1 day", date_labels = "%m/%d/%y", expand = c(0, 0, 0, 0)) +
    scale_fill_manual(name = "Status", values = c("Not Safe" = "red", "At Risk" = "orange", "Safe" = "green"), breaks=c("Not Safe","At Risk","Safe")) +
    scale_alpha_manual(name = "Status", values = c("Not Safe" = 0.15, "At Risk" = 0.15, "Safe" = 0.15), breaks=c("Not Safe","At Risk","Safe")) +
    scale_color_manual(name = "Setting", values = mshs_colors)
}
```

```{r Custom function for graphing resulted lab volume stratified by order priority for Clinical Pathology, echo = FALSE, warning = FALSE, message = FALSE}

# Function for plotting total resulted lab volume stratified by order priority
cp_resulted_volume_graph <- function(data, test_name, site_name) {
  ggplot() +
    geom_point(data = data[data$ResultDate >= start_date & data$Test == test_name & data$Site == site_name, ], aes(x = ResultDate, y = ResultedVolume, color = DashboardPriority, shape = DashboardPriority), size = 3) +
    geom_line(data = data[data$ResultDate >= start_date & data$Test == test_name & data$Site == site_name, ], aes(x = ResultDate, y = ResultedVolume, color = DashboardPriority), linetype = "dashed") +
    labs(title = paste0(site_name, " ", test_name, " Resulted Lab Volume"), x = "Date",  y = "Volume of Labs", color = "Priority", shape = "Priority") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal", legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8),axis.text.x = element_text(angle = 30, hjust = 1)) +
    scale_x_date(limits = c(start_date -1, max(data$ResultDate)+1), breaks = seq(start_date, max(data$ResultDate), by = 3), date_minor_breaks = "1 day", date_labels = "%m/%d/%y", expand = c(0, 0, 0, 0)) +
    # scale_y_continuous(sec.axis = sec_axis(~.*1, name = " ", breaks = NULL, label = NULL)) +
    scale_color_manual(name = "Priority", values = mshs_colors)
}
```

```{r Custom function for plotting TAT percentages and resulted volume on single graph for Clinical Pathology, echo = FALSE, warning = FALSE, message = FALSE}

cp_tat_and_volume_plot <- function(data_tat, test_name, site_name, lab_priority, metric) {
  # 
  # Subset turnaround time and volume data based on test, site, and priority
  data_tat_plot <- data_tat %>%
    filter(ResultDate >= start_date & 
             Test == test_name & 
             Site == site_name & 
             DashboardPriority == lab_priority)

  data_vol_plot <- cp_dashboard_vol_summary %>%
    filter(ResultDate >= start_date & 
             Test == test_name & 
             Site == site_name & 
             DashboardPriority == lab_priority)
  # 
  # Create printable metric name based on selected metric
  metric_name <- ifelse(metric == "ReceiveResultPercent", "Receive to Result", ifelse(metric == "CollectResultPercent", "Collect to Result", "Error"))
  #
  # Determine scale factor for secondary axis based on maximum resulted volume
  base10 <- floor(log10(max(data_vol_plot$ResultedVolume)))
  scale <- ceiling(max(data_vol_plot$ResultedVolume)/(10^(base10-1)))*10^(base10-1)
  #
  # Create plot and standard settings
  ggplot() +
    # Plot safe, at risk, not safe thresholds
    geom_rect(aes(xmin = start_date - 1, xmax = max(data_tat_plot$ResultDate) + 1, 
                  ymin = -Inf, ymax = min(data_tat_plot$NotSafeThreshold), 
                  fill = "Not Safe", alpha = "Not Safe")) +
    geom_rect(aes(xmin = start_date - 1, xmax = max(data_tat_plot$ResultDate) + 1, 
                  ymin = min(data_tat_plot$NotSafeThreshold), ymax = min(data_tat_plot$SafeThreshold), 
                  fill = "At Risk", alpha = "At Risk"), show.legend = FALSE) +
    geom_rect(aes(xmin = start_date - 1, xmax = max(data_tat_plot$ResultDate) + 1, 
                  ymin = min(data_tat_plot$SafeThreshold), ymax = 1, 
                  fill = "Safe", alpha = "Safe"), show.legend = FALSE) + 
    geom_rect(aes(xmin = start_date - 1, xmax = max(data_tat_plot$ResultDate) + 1, 
                  ymin = 1, ymax = Inf, fill = "N/A", 
                  alpha = "N/A"), show.legend = FALSE) +
    # Plot percentage of labs within turnaround time target
    geom_point(data = data_tat_plot, aes_string(x = "ResultDate", y = metric, color = "DashboardSetting", shape = "DashboardSetting"), size = 3) +
    geom_line(data = data_tat_plot, aes_string(x = "ResultDate", y = metric, color = "DashboardSetting"), linetype = "dashed") +
    # Plot resulted volume on secondary axis
    geom_point(data = data_vol_plot, aes(x = ResultDate, y = ResultedVolume/scale, size = "Volume"), color = "#959595", shape = 18) +
    geom_line(data = data_vol_plot, aes(x = ResultDate, y = ResultedVolume/scale, linetype = "Volume"), color = "#959595") +
    # Specify graph labels and themes
    labs(title = paste0(site_name, " ", test_name, " ", metric_name, ":\n", "Percentage of ", lab_priority, " Labs within Target TAT"), 
         x = "Date",  y = "Percentage of Labs", color = "Setting", shape = "Setting", fill = "Status", alpha = "Status", linetype = "Resulted Volume", size = "Resulted Volume") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal", 
          legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8),
          axis.text.x = element_text(angle = 30, hjust = 1)) +
    # Specify fills, shapes, and lines mappings and legends
    scale_fill_manual(name = "Status", values = c("Not Safe" = "red", "At Risk" = "orange", "Safe" = "green", "N/A" = "grey"), 
                      breaks=c("Not Safe","At Risk","Safe")) +
    scale_alpha_manual(name = "Status", values = c("Not Safe" = 0.25, "At Risk" = 0.25, "Safe" = 0.25, "N/A" = 0.5), 
                       breaks=c("Not Safe","At Risk","Safe")) +
    scale_color_manual(name = "Setting", values = mshs_colors) +
    scale_size_manual(name = "Resulted Volume", values = 2, labels = paste(lab_priority, "Labs, \n All Settings")) + 
    scale_linetype_manual(name = "Resulted Volume", values = "dotted", labels = paste(lab_priority, "Labs, \n All Settings")) +
    # Reorder legends
    guides(color = guide_legend(order = 1, nrow = length(unique(data_tat_plot$DashboardSetting)), title.vjust = 1), shape = guide_legend(order = 1, nrow = length(unique(data_tat_plot$DashboardSetting)), title.vjust = 1), fill = guide_legend(order = 3, nrow = 3, title.vjust = 1), alpha = guide_legend(order = 3, nrow = 3, title.vjust = 1), 
           size = guide_legend(order = 2, title.vjust = 1), linetype = guide_legend(order = 2, title.vjust = 1)) +
    # Specify axis properties
    scale_x_date(limits = c(start_date -1, max(data_tat_plot$ResultDate)+1), 
                 breaks = seq(start_date, max(data_tat_plot$ResultDate), by = 3), date_minor_breaks = "1 day", 
                 date_labels = "%m/%d/%y", expand = c(0, 0, 0, 0)) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(from = 0, to = 1, length.out = 5), expand = c(0, 0, 0.05, 0), labels = percent_format(accuracy = 1), 
                       sec.axis = sec_axis(~.*scale, name = "Volume of Labs"))
}
```


```{r Custom function for stepping through stratified TAT data for Clinical Pathology, echo = FALSE, warning = FALSE, message = FALSE}
cp_stratified_data_for_plots <- function(tat_data, test) {
  test_df <- tat_data %>% 
    filter(Test == test,
           ResultDate >= start_date)
  sites <- unique(test_df$Site)
  for (site in sites) {
    site_df <- test_df %>%
      filter(Site == site)
    priorities <- unique(site_df$DashboardPriority)
    for (priority in priorities) {
      priority_df <- site_df %>%
        filter(DashboardPriority == priority)
      # print(tat_percentage_graph(data = priority_df, test_name = test, site_name = site, lab_priority = priority, metric = "ReceiveResultPercent"))
      # print(tat_percentage_graph(data = priority_df, test_name = test, site_name = site, lab_priority = priority, metric = "CollectResultPercent"))
      print(cp_tat_and_volume_plot(data_tat = priority_df, test_name = test, site_name = site, lab_priority = priority, metric = "ReceiveResultPercent"))
      print(cp_tat_and_volume_plot(data_tat = priority_df, test_name = test, site_name = site, lab_priority = priority, metric = "CollectResultPercent"))
      }
    print(cp_resulted_volume_graph(data = cp_dashboard_vol_summary, test_name = test, site_name = site))
  }
}
```


```{r Summarize data to calculate defects and defect rates for Clinical Pathology, echo = FALSE, warning = FALSE, message = FALSE}

# Summarize data based on site and priority
cp_dashboard_defect_summary <- cp_dashboard_tat_filter %>%
  group_by(Site, ResultDate, Division, Test, DashboardPriority) %>%
  summarize(ResultedVolume = sum(ResultedVolume), 
            ResultedVolumeWithTAT = sum(ResultedVolumeWithTAT),
            ReceiveResultInTarget = sum(ReceiveResultInTarget), 
            CollectResultInTarget = sum(CollectResultInTarget),
            ReceiveResultDefects = ResultedVolumeWithTAT - ReceiveResultInTarget, 
            ReceiveResultDefectRate = ReceiveResultDefects / ResultedVolumeWithTAT)

cp_dashboard_defect_summary <- cp_dashboard_defect_summary[!is.na(cp_dashboard_defect_summary$ReceiveResultDefectRate), ]
```

```{r Custom function for p-charts for Clinical Pathology, echo = FALSE, warning = FALSE, message = FALSE}

cp_receive_result_pchart <- function(data_defect, test_name, site_name, lab_priority) {
  # 
  # Subset turnaround time and volume data based on test, site, and priority
  data_defect_plot <- data_defect %>%
    filter(ResultDate >= start_date & 
             Test == test_name & 
             Site == site_name & 
             DashboardPriority == lab_priority)
  # Calculate center line
  center_line <- mean(QC_Lines(data = data_defect_plot$ReceiveResultDefectRate, n = data_defect_plot$ResultedVolumeWithTAT, method = "p")$pBar)
  # 
  # Create plot and standard settings
  ggplot(data = data_defect_plot, aes(x = ResultDate, y = ReceiveResultDefectRate, n = ResultedVolumeWithTAT)) +
  # Create point and connecting lines for defect rate data
  geom_point(color = mshs_colors[1], shape = 16, size = 3) +
  geom_line(color = mshs_colors[1], linetype = "dashed") +
  # Add centerline, upper, and lower control limit lines
  stat_QC(method = "p", auto.label = T, color.qc_center = "black") +
  geom_label(x = max(data_defect_plot$ResultDate)+1, y = center_line, vjust = 1.2, hjust = 1, label = paste("CL:", percent(center_line, accuracy = 0.1))) +
  # Specify graph labels and themes
  labs(title = paste(site_name, test_name, lab_priority, "Labs:\n", "Control Chart of Non-Compliant Receive to Result TAT"), x = "Date",  y = "Percent Non-Compliant") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal", 
          legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8),
          axis.text.x = element_text(angle = 30, hjust = 1)) +
  # Specify axis properties
  scale_x_date(limits = c(start_date -1, max(data_defect_plot$ResultDate)+1), breaks = seq(start_date, max(data_defect_plot$ResultDate), by = 3), date_minor_breaks = "1 day", date_labels = "%m/%d/%y", expand = c(0, 0, 0, 0)) +
  scale_y_continuous(labels = percent_format(accuracy = 1))
}


```

```{r Iterate through defect rate data and plot p-charts for Clinical Pathology, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'}

cp_stratified_data_for_pcharts <- function(defect_data, test) {
  test_df <- defect_data %>%
    filter(Test == test & 
             ResultDate >= start_date)
  sites <- unique(test_df$Site)

  for (site in sites) {
    # print(site)
    # print(test)
    site_df <- test_df %>%
      filter(Site == site)
    priorities <- unique(site_df$DashboardPriority)
    for (priority in priorities) {
      # print(priority)
      priority_df <- site_df %>%
        filter(DashboardPriority == priority)
      # Determine average resulted volume over last 30 days to see if p-chart is valid
      avg_resulted_volume <- mean(priority_df$ResultedVolumeWithTAT[priority_df$ResultDate >= start_date])
      # print(avg_resulted_volume)
      if (avg_resulted_volume >= 50) {
        print(cp_receive_result_pchart(data_defect = priority_df, test_name = test, site_name = site, lab_priority = priority))
      } else {
        cat(paste('\n<center><h3><i>', site, test, priority, "Labs: Insufficient volume for this analysis (n<50).</h3> \n <h4>(Average resulted volume over last 30 days:", round(avg_resulted_volume, digits = 0), "specimens.)", '</i></h4></center>\n\n<br><br>'))
      }
    }
  }
}

```


```{r Format Anatomic Pathology historical repository for plotting, warning = FALSE, message = FALSE, echo = FALSE}
#Exclude weekends
AP_historical_repo_weekdays <- AP_historical_repo[which(AP_historical_repo$Signed_out_day_only != "Sunday" & AP_historical_repo$Signed_out_day_only != "Saturday" & AP_historical_repo$Patient_setting != "NA"),]

# Convert characters to factors

AP_historical_repo_weekdays$Signed_out_date_only <- as.Date(AP_historical_repo_weekdays$Signed_out_date_only)
AP_historical_repo_weekdays$Lab_metric_within_target <- as.numeric(AP_historical_repo_weekdays$Lab_metric_within_target)
AP_historical_repo_weekdays$Patient_metric_avg <- as.numeric(AP_historical_repo_weekdays$Patient_metric_avg)
AP_historical_repo_weekdays$Lab_metric_avg <- as.numeric(AP_historical_repo_weekdays$Lab_metric_avg)

#Calculate the total none defects
AP_historical_repo_weekdays$total_none_defects <- round(AP_historical_repo_weekdays$Lab_metric_within_target * AP_historical_repo_weekdays$No_cases_signed_out)

#Calculate the total defects
AP_historical_repo_weekdays$total_defects <- AP_historical_repo_weekdays$No_cases_signed_out - AP_historical_repo_weekdays$total_none_defects 

#Standardize Facility name 
AP_historical_repo_weekdays$Facility_Old <- AP_historical_repo_weekdays$Facility

AP_historical_repo_weekdays$Facility[AP_historical_repo_weekdays$Facility == "BIMC"] <- "MSBI"
AP_historical_repo_weekdays$Facility[AP_historical_repo_weekdays$Facility == "R"] <- "MSW"
AP_historical_repo_weekdays$Facility[AP_historical_repo_weekdays$Facility == "SL"] <- "MSSL"
AP_historical_repo_weekdays$Facility[AP_historical_repo_weekdays$Facility == "KH"] <- "MSB"

#Add an extra column to change the facilities for GYN and CYTO GYN for receive to result to Centralized Lab
AP_historical_repo_weekdays$New_Facility_RTR_CYTO <- AP_historical_repo_weekdays$Facility

AP_historical_repo_weekdays[(AP_historical_repo_weekdays$Spec_group == "CYTO GYN" | AP_historical_repo_weekdays$Spec_group == "CYTO NONGYN"),]$New_Facility_RTR_CYTO <- "Centralized Lab"

ap_site_order <- c("MSH", "MSQ", "MSBI","PACC", "MSB", "MSW", "MSSL", "NYEE")
ap_site_order_RTR <- c("Centralized Lab","MSH", "MSQ", "MSBI","PACC", "MSB", "MSW", "MSSL", "NYEE")

AP_historical_repo_weekdays$Facility <- factor(AP_historical_repo_weekdays$Facility , levels = ap_site_order)

AP_historical_repo_weekdays$New_Facility_RTR_CYTO <- factor(AP_historical_repo_weekdays$New_Facility_RTR_CYTO, levels = ap_site_order_RTR )

#determine the 30 business that will be reported
ap_unique_dates <- unique(AP_historical_repo_weekdays$Signed_out_date_only)

ap_ordered_dates <- ap_unique_dates[rev(order(ap_unique_dates))]

ap_reporting_30_day_period <- ap_ordered_dates[1:30]
ap_first_day_in_reporting_period <- ap_ordered_dates[30] 
ap_last_day_in_reporting_period <- ap_ordered_dates[1]

ap_historical_30_day_period <- AP_historical_repo_weekdays[which(AP_historical_repo_weekdays$Signed_out_date_only>=ap_first_day_in_reporting_period),]

#summarized the data to plot it correctly
ap_historical_30_day_period_sum_RTR <-summarise(group_by(ap_historical_30_day_period, Signed_out_date_only,Spec_group, New_Facility_RTR_CYTO,Patient_setting), Lab_metric_within_target = format(round(mean(as.numeric(Lab_metric_within_target), na.rm = TRUE), 2)), Patient_metric_avg = format(round(mean(as.numeric(Patient_metric_avg), na.rm = TRUE),0)),No_cases_signed_out = sum(No_cases_signed_out))

ap_historical_30_day_period_sum_RTR[c("Lab_metric_within_target", "Patient_metric_avg", "No_cases_signed_out")] <- lapply(ap_historical_30_day_period_sum_RTR[c("Lab_metric_within_target", "Patient_metric_avg", "No_cases_signed_out")], as.numeric)

ap_historical_30_day_period_sum_CTR <-summarise(group_by(ap_historical_30_day_period, Signed_out_date_only,Spec_group, Facility, Patient_setting), Lab_metric_within_target = format(round(mean(as.numeric(Lab_metric_within_target), na.rm = TRUE), 2)), Patient_metric_avg = format(round(mean(as.numeric(Patient_metric_avg), na.rm = TRUE),0)),No_cases_signed_out = sum(No_cases_signed_out))

ap_historical_30_day_period_sum_CTR[c("Lab_metric_within_target", "Patient_metric_avg", "No_cases_signed_out")] <- lapply(ap_historical_30_day_period_sum_CTR[c("Lab_metric_within_target", "Patient_metric_avg", "No_cases_signed_out")], as.numeric)

ap_historical_30_day_period_sum_vol <-summarise(group_by(ap_historical_30_day_period, Signed_out_date_only,Spec_group, New_Facility_RTR_CYTO),No_cases_signed_out = sum(No_cases_signed_out))

ap_historical_30_day_period_sum_vol_CTR <-summarise(group_by(ap_historical_30_day_period, Signed_out_date_only,Spec_group, Facility),No_cases_signed_out = sum(No_cases_signed_out))

```


```{r Anatomic Pathology: plot volume and % TAT within target, warning = FALSE, message = FALSE, echo = FALSE}

#we need to create a percent within target graph for cyto and patho
#the graph will have the split between IP and AMB

ap_lab_TAT_volume_plot <- function(ap_historical_30_day_period_sum_RTR, ap_historical_30_day_period_sum_vol, test_name, site_name, metric) {
  
  ap_data_tat <- ap_historical_30_day_period_sum_RTR[ap_historical_30_day_period_sum_RTR$Spec_group == test_name & ap_historical_30_day_period_sum_RTR$New_Facility_RTR_CYTO == site_name,]
  
  ap_data_vol <- ap_historical_30_day_period_sum_vol[ap_historical_30_day_period_sum_vol$Spec_group == test_name & ap_historical_30_day_period_sum_vol$New_Facility_RTR_CYTO == site_name,]
 
  # Create printable metric name based on selected metric
  metric_name <- ifelse(metric == "Lab_metric_within_target", "Receive to Result", ifelse(metric == "Patient_metric_avg", "Collect to Result", "Error"))
  # Create printable test name based on selected test
  test_name <- ifelse(test_name == "Breast", "All Breast Specimen", ifelse(metric == "GI", "GI Biopsies", test_name))
  
ggplot() +
  # Plot safe, at risk, not safe thresholds
  geom_rect(aes(xmin = ap_first_day_in_reporting_period - 1, xmax = ap_last_day_in_reporting_period + 1, ymin = -Inf, ymax = 0.8, fill = "Not Safe", alpha = "Not Safe"))+
  geom_rect(aes(xmin = ap_first_day_in_reporting_period - 1, xmax = ap_last_day_in_reporting_period + 1, ymin = 0.8, ymax = 0.9, fill = "At Risk",  alpha = "At Risk"))+
  geom_rect(aes(xmin = ap_first_day_in_reporting_period - 1, xmax = ap_last_day_in_reporting_period + 1, ymin = 0.9, ymax = Inf, fill = "Safe", alpha = "Safe"))+  
  geom_rect(aes(xmin = ap_first_day_in_reporting_period - 1, xmax = ap_last_day_in_reporting_period + 1, ymin = 0.9, ymax = Inf, fill = "N/A", alpha = "N/A"), show.legend = FALSE)+ 

  # Plot resulted volume on secondary axis
  geom_point(data = ap_data_vol, aes(x = Signed_out_date_only, y = No_cases_signed_out/max(No_cases_signed_out), size = "Spec_group"), shape = 18, color = "#959595")+
  geom_line(data = ap_data_vol, aes(x = Signed_out_date_only, y = No_cases_signed_out/max(No_cases_signed_out),linetype = "Spec_group"), color = "#959595")+
  
  # Plot percentage of labs within turnaround time target
  geom_point(data = ap_data_tat, aes_string(x = "Signed_out_date_only", y = metric, shape = "Patient_setting", color = "Patient_setting"), size = 3)+
  geom_line(data = ap_data_tat, aes_string(x = "Signed_out_date_only", y = metric, shape = "Patient_setting", color = "Patient_setting"), linetype = "dashed")+
  
  # Specify graph labels and themes
  labs(title = paste0(site_name, " ", test_name, " ", metric_name, ":\n", "Percentage of Labs within Target TAT"), 
       x = "Date",  y = "Percentage of Labs", color = "Setting", shape = "Setting", fill = "Status", alpha = "Status", linetype = "Resulted Volume", size = "Resulted Volume") +
  
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal", 
        legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8),
        axis.text.x = element_text(angle = 30, hjust = 1)) +
 
  # Specify fills, shapes, and lines mappings and legends
  scale_fill_manual(name = "Status", values = c("Not Safe" = "red", "At Risk" = "orange", "Safe" = "green", "N/A" = "grey"), breaks=c("Not Safe","At Risk","Safe")) +
  scale_alpha_manual(name = "Status", values = c("Not Safe" = 0.25, "At Risk" = 0.25, "Safe" = 0.25, "N/A" = 0.5), breaks=c("Not Safe","At Risk","Safe")) +
  
  scale_color_manual(name = "Setting", values = mshs_colors) +
  scale_size_manual(name = "Resulted Volume", values = 2, labels = paste("All Labs, \n All Settings")) + 
  scale_linetype_manual(name = "Resulted Volume", values = "dotted", labels = paste("All Labs, \n All Settings"))+
  
  # Reorder legends
  guides(color = guide_legend(order = 1, nrow = length(unique(ap_data_tat$Patient_setting)), title.vjust = 1), shape = guide_legend(order = 1, nrow = length(unique(ap_data_tat$Patient_setting)), title.vjust = 1), fill = guide_legend(order = 3, nrow = 3, title.vjust = 1), alpha = guide_legend(order = 3, nrow = 3, title.vjust = 1), size = guide_legend(order = 2, title.vjust = 1), linetype = guide_legend(order = 2, title.vjust = 1)) +
  
  # Specify axis properties
  scale_x_date(name = "Date", labels = date_format("%m/%d/%Y"), limits = c(ap_first_day_in_reporting_period - 1,ap_last_day_in_reporting_period + 1), date_breaks = "3 days", date_minor_breaks = "1 day", expand = c(0, 0, 0, 0))+
  scale_y_continuous(name = "Percentage of Labs",limits = c(0,1), labels = percent, sec.axis = sec_axis(~.*max(ap_data_vol$No_cases_signed_out), name = "Volume of Labs"))

}



#lab_TAT_volume_AP_plot(historical_30_day_period_sum, historical_30_day_period_sum_vol, "CYTO GYN", "Centralized Lab", "Lab_metric_within_target")

```


```{r Anatomic Pathology: Avg TAT for patient metric, warning = FALSE, message = FALSE, echo = FALSE}

#we need to create a percent within target graph for cyto and patho
#the graph will have the split between IP and AMB

ap_patient_TAT_plot <- function(ap_historical_30_day_period_sum_CTR, ap_historical_30_day_period_sum_vol_CTR, test_name, site_name, metric) {
  
  ap_data_tat <- ap_historical_30_day_period_sum_CTR[ap_historical_30_day_period_sum_CTR$Spec_group == test_name & ap_historical_30_day_period_sum_CTR$Facility == site_name,]
  
  ap_data_vol <- ap_historical_30_day_period_sum_vol_CTR[ap_historical_30_day_period_sum_vol_CTR$Spec_group == test_name & ap_historical_30_day_period_sum_vol_CTR$Facility == site_name,]
  
  # Create printable metric name based on selected metric
  metric_name <- ifelse(metric == "Lab_metric_within_target", "Receive to Result", ifelse(metric == "Patient_metric_avg", "Collect to Result", "Error"))
  # Create printable test name based on selected test
  test_name <- ifelse(test_name == "Breast", "All Breast Specimen", ifelse(test_name == "GI", "GI Biopsies", test_name))

  ggplot() +

  # Plot resulted volume on secondary axis
  geom_point(data = ap_data_vol, aes(x = Signed_out_date_only, y = No_cases_signed_out/mean(No_cases_signed_out) , size = "Spec_group"), shape = 18, color = "#959595")+
  geom_line(data = ap_data_vol, aes(x = Signed_out_date_only, y = No_cases_signed_out/mean(No_cases_signed_out),linetype = "Spec_group"), color = "#959595")+
    
  # Plot Average lab metric TAT
  geom_point(data = ap_data_tat, aes_string(x = "Signed_out_date_only", y = metric, shape = "Patient_setting", color = "Patient_setting"), size = 3)+
  geom_line(data = ap_data_tat, aes_string(x = "Signed_out_date_only", y = metric, shape = "Patient_setting", color = "Patient_setting"), linetype = "dashed")+
  
  # Specify graph labels and themes
  labs(title = paste0(site_name, " ", test_name, " ", metric_name,":\n","Average TAT (Days)"), 
       x = "Date",  y = "Percentage of Labs", color = "Setting", shape = "Setting", linetype = "Resulted Volume", size = "Resulted Volume") +
  
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal", 
        legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8),
        axis.text.x = element_text(angle = 30, hjust = 1)) +
 
  # Specify fills, shapes, and lines mappings and legends
  scale_color_manual(name = "Setting", values = mshs_colors) +
  scale_size_manual(name = "Resulted Volume", values = 2, labels = paste("All Labs, \n All Settings")) + 
  scale_linetype_manual(name = "Resulted Volume", values = "dotted", labels = paste("All Labs, \n All Settings"))+
  
  # Reorder legends
  guides(color = guide_legend(order = 1, nrow = length(unique(ap_data_tat$Patient_setting)), title.vjust = 1), shape = guide_legend(order = 1, nrow = length(unique(ap_data_tat$Patient_setting)), title.vjust = 1), size = guide_legend(order = 2, title.vjust = 1), linetype = guide_legend(order = 2, title.vjust = 1)) +
  
  # Specify axis properties
  scale_x_date(name = "Date", labels = date_format("%m/%d/%Y"), limits = c(ap_first_day_in_reporting_period - 1,ap_last_day_in_reporting_period + 1), date_breaks = "3 days", date_minor_breaks = "1 day", expand = c(0, 0, 0, 0))+
  
  scale_y_continuous(name = "Average TAT (Days)",limits = c(0,max(ap_data_tat$Patient_metric_avg+1)), sec.axis = sec_axis(~.*mean(ap_data_vol$No_cases_signed_out), name = "Volume of Labs"))

}



#patient_TAT_AP_plot(historical_30_day_period_sum,"CYTO GYN", "MSH", "Patient_metric_avg")

```


```{r Custom function for graphing resulted lab volume, echo = FALSE, warning = FALSE, message = FALSE}
# Function for plotting total resulted lab volume

ap_resulted_volume_graph <- function(ap_historical_30_day_period_sum_vol, test_name, site_name) {
  
  ap_data_vol <- ap_historical_30_day_period_sum_vol[ap_historical_30_day_period_sum_vol$Spec_group == test_name & ap_historical_30_day_period_sum_vol$New_Facility_RTR_CYTO == site_name,]

  # Create printable test name based on selected test
  test_name <- ifelse(test_name == "Breast", "All Breast Specimen", ifelse(test_name == "GI", "GI Biopsies", test_name))

  ggplot() +
    geom_point(data = ap_data_vol, aes(x = Signed_out_date_only, y = No_cases_signed_out, size = "Spec_group"), shape = 16, color = mshs_colors[1]) +
    geom_line(data = ap_data_vol, aes(x = Signed_out_date_only, y = No_cases_signed_out, linetype = "Spec_group"), color = mshs_colors[1]) +
    labs(title = paste0(site_name, " ", test_name, " Resulted Lab Volume"), x = "Date",  y = "Volume of Labs", color = "Setting", shape = "Setting") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal", legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8),axis.text.x = element_text(angle = 30, hjust = 1)) +
    scale_x_date(name = "Date", labels = date_format("%m/%d/%Y"), limits = c(ap_first_day_in_reporting_period - 1,ap_last_day_in_reporting_period + 1), date_breaks = "3 days", date_minor_breaks = "1 day", expand = c(0, 0, 0, 0))+
    scale_size_manual(name = "Resulted Volume", values = 2, labels = paste("All Labs, \n All Settings")) + 
    scale_linetype_manual(name = "Resulted Volume", values = "dotted", labels = paste("All Labs, \n All Settings"))+
    scale_y_continuous(limits = c(min(ap_data_vol$No_cases_signed_out-1),max(ap_data_vol$No_cases_signed_out+1)))
}

#resulted_volume_graph(historical_30_day_period_sum_vol, "CYTO NONGYN", "Centralized Lab")

```

```{r function to go through all the facilities for each test, warning = FALSE, message = FALSE, echo = FALSE}

ap_stratified_data_for_charts <- function(ap_historical_30_day_period_sum_RTR, ap_historical_30_day_period_sum_CTR, ap_historical_30_day_period_sum_vol, test_name){
  
  sites_RTR <- unique(ap_historical_30_day_period_sum_RTR[ap_historical_30_day_period_sum_RTR$Spec_group == test_name,]$New_Facility_RTR_CYTO)
  
  sites_CTR <- unique(ap_historical_30_day_period_sum_CTR[ap_historical_30_day_period_sum_CTR$Spec_group == test_name,]$Facility)

  for (site_RTR in sites_RTR){
    
    print(ap_lab_TAT_volume_plot(ap_historical_30_day_period_sum_RTR = ap_historical_30_day_period_sum_RTR, ap_historical_30_day_period_sum_vol = ap_historical_30_day_period_sum_vol, test_name = test_name, site_name = site_RTR, metric = "Lab_metric_within_target"))
  }
  
  for (site_CTR in sites_CTR){
    print(ap_patient_TAT_plot(ap_historical_30_day_period_sum_CTR = ap_historical_30_day_period_sum_CTR, ap_historical_30_day_period_sum_vol_CTR = ap_historical_30_day_period_sum_vol_CTR, test_name = test_name, site_name = site_CTR, metric = "Patient_metric_avg"))
  }
  
  for (site_RTR in sites_RTR){
    print(ap_resulted_volume_graph(ap_historical_30_day_period_sum_vol = ap_historical_30_day_period_sum_vol, test_name = test_name, site_name = site_RTR))
  }
}
  
#stratified_data_for_AP_charts(historical_30_day_period_sum_RTR, historical_30_day_period_sum_CTR, historical_30_day_period_sum_vol, "CYTO GYN")


```



```{r summarize data to calculate defects and defect rates for anatomic pathology, warning = FALSE, message = FALSE, echo = FALSE}

ap_historical_30_day_period_defects <-summarise(group_by(ap_historical_30_day_period, Signed_out_date_only,Spec_group, New_Facility_RTR_CYTO), No_cases_signed_out = sum(No_cases_signed_out),total_none_defects = sum(total_none_defects), total_defects = sum(total_defects), defective_rate = total_defects/No_cases_signed_out)

```

```{r function for defective rate p-charts for anatomic pathology, echo = FALSE, warning = FALSE, message = FALSE}
ap_defective_rate_pchart <- function(ap_historical_30_day_period_defects, test_name, site_name) {
  
  ap_data_defc <- ap_historical_30_day_period_defects[ap_historical_30_day_period_defects$Spec_group == test_name & ap_historical_30_day_period_defects$New_Facility_RTR_CYTO == site_name,]
  
  # Create printable test name based on selected test
  test_name <- ifelse(test_name == "Breast", "All Breast Specimen", ifelse(test_name == "GI", "GI Biopsies", test_name))
   
  # Find the center line for the p-chart using QC_lines 
  center_line <- mean(QC_Lines(data = ap_data_defc$defective_rate, n = ap_data_defc$No_cases_signed_out, method = "p")$pBar)
  
  # Create plot and standard settings
  ggplot(data = ap_data_defc, aes(x = Signed_out_date_only, y = defective_rate, n = No_cases_signed_out)) +
  # Create point and connecting lines for defect rate data
  geom_point(color = mshs_colors[1], shape = 16, size = 3) +
  geom_line(color = mshs_colors[1], linetype = "dashed") +
  
  # Add centerline, upper, and lower control limit lines
  stat_QC(method = "p", auto.label = TRUE, color.qc_center = "black", limit.txt.label = c("LCL", "UCL")) +
  geom_label(x = max(ap_data_defc$Signed_out_date_only)+1, y = center_line, vjust = 1.2, hjust = 1, label = paste("CL:", percent(center_line, accuracy = 0.1))) +
  # Specify graph labels and themes
  labs(title = paste(site_name, test_name, "All Labs:\n", "Control Chart of Non-Compliant Receive to Result TAT"), x = "Date",  y = "Percent Non-Compliant") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal", 
          legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8),
          axis.text.x = element_text(angle = 30, hjust = 1)) +
  # Specify axis properties
  scale_x_date(limits = c(ap_first_day_in_reporting_period -1, max(ap_data_defc$Signed_out_date_only)+1), breaks = seq(ap_first_day_in_reporting_period, max(ap_data_defc$Signed_out_date_only), by = 3), date_minor_breaks = "1 day", date_labels = "%m/%d/%y", expand = c(0, 0, 0, 0)) +
  scale_y_continuous(labels = percent_format(accuracy = 1))
}

#defective_rate_pchart(historical_30_day_period_defects, "CYTO GYN", "Centralized Lab")

```

```{r function to go through all the facilities for each test for the p-chart, warning = FALSE, message = FALSE, echo = FALSE, results = 'asis'}

ap_stratified_data_for_p_charts <- function(ap_historical_30_day_period_defects, test_name){
  
  sites <- unique(ap_historical_30_day_period_defects[ap_historical_30_day_period_defects$Spec_group == test_name,]$New_Facility_RTR_CYTO)
    
  for (site in sites){
    
    ap_avg_resulted_volume <- mean(ap_historical_30_day_period_defects[(ap_historical_30_day_period_defects$New_Facility_RTR_CYTO==site & ap_historical_30_day_period_defects$Spec_group==test_name),]$No_cases_signed_out)
    
    if (ap_avg_resulted_volume >= 50){
      print(ap_defective_rate_pchart(ap_historical_30_day_period_defects = ap_historical_30_day_period_defects, test_name = test_name, site_name = site))
    }
    else{
      # Create printable test name based on selected test
      test_name_new <- ifelse(test_name == "Breast", "All Breast Specimen", ifelse(test_name == "GI", "GI Biopsies", test_name))
      cat(paste('\n<center><h3><i>', site, test_name_new, "Labs: Insufficient volume for this analysis (n<50).</h3> \n <h4>(Average resulted volume over last 30 days:", round(ap_avg_resulted_volume, digits = 0), "specimens.)", '</i></h4></center>\n\n<br><br>'))
    }
  }
}

  
#stratified_data_for_AP_p_charts(historical_30_day_period_defects, "CYTO NONGYN")

```
# {.tabset}

## Efficiency Indicator Historical Performance {.tabset}

### Troponin
```{r Troponin historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
cp_stratified_data_for_plots(tat_data = cp_dashboard_tat_filter, test = "Troponin")
```
<h6> TAT percentages include ED, ICU, and IP Non-ICU labs with valid turnaround times. Resulted volumes include all resulted labs from all settings, including Ambulatory. </h6>

### Lactate WB
```{r Lactate WB historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
cp_stratified_data_for_plots(tat_data = cp_dashboard_tat_filter, test = "Lactate WB")
```
<h6> TAT percentages include ED, ICU, and IP Non-ICU labs with valid turnaround times. Resulted volumes include all resulted labs from all settings, including Ambulatory. </h6>

### BUN
```{r BUN historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
cp_stratified_data_for_plots(tat_data = cp_dashboard_tat_filter, test = "BUN")
```
<h6> TAT percentages include ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Resulted volumes include all resulted labs from all settings. </h6>

### HGB
```{r HGB historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
cp_stratified_data_for_plots(tat_data = cp_dashboard_tat_filter, test = "HGB")
```
<h6> TAT percentages include ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Resulted volumes include all resulted labs from all settings. </h6>

### PT
```{r PT historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
cp_stratified_data_for_plots(tat_data = cp_dashboard_tat_filter, test = "PT")
```
<h6> TAT percentages include ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Resulted volumes include all resulted labs from all settings. </h6>

### Rapid Flu
```{r Rapid Flu historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
cp_stratified_data_for_plots(tat_data = cp_dashboard_tat_filter, test = "Rapid Flu")
```
<h6> TAT percentages include ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Resulted volumes include all resulted labs from all settings. </h6>

### C. diff
```{r C. diff historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
cp_stratified_data_for_plots(tat_data = cp_dashboard_tat_filter, test = "C. diff")
```
<h6> TAT percentages include ED, ICU, and IP Non-ICU labs with valid turnaround times. Resulted volumes include all resulted labs from all settings. </h6>

### All Breast Specimens
```{r All Breast Specimens historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}

ap_stratified_data_for_charts(ap_historical_30_day_period_sum_RTR, ap_historical_30_day_period_sum_CTR, ap_historical_30_day_period_sum_vol, "Breast")

```

### GI Biopsies
```{r GI Biopsies historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}

ap_stratified_data_for_charts(ap_historical_30_day_period_sum_RTR, ap_historical_30_day_period_sum_CTR, ap_historical_30_day_period_sum_vol, "GI")

```

### Cyto Gyn Specimens
<h1><span style = "color:red">Cyto Gyn Pending - Resolution of Data Issues</h1>
```{r Cyto Gyn Specimens historical data, eval = FALSE, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}

ap_stratified_data_for_charts(ap_historical_30_day_period_sum_RTR, ap_historical_30_day_period_sum_CTR, ap_historical_30_day_period_sum_vol, "CYTO GYN")

```

### Cyto Non-Gyn Specimens
```{r Cyto Non-Gyn Specimens historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}

ap_stratified_data_for_charts(ap_historical_30_day_period_sum_RTR, ap_historical_30_day_period_sum_CTR, ap_historical_30_day_period_sum_vol, "CYTO NONGYN")

```

## Control Charts of Non-Compliant Labs {.tabset}
### Troponin
```{r Troponin p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'}
cp_stratified_data_for_pcharts(defect_data = cp_dashboard_defect_summary, test = "Troponin")
```
<h6> Control charts includes ED, ICU, and IP Non-ICU labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$.


### Lactate WB
```{r Lactate WB p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'}
cp_stratified_data_for_pcharts(defect_data = cp_dashboard_defect_summary, test = "Lactate WB")
```
<h6> Control charts includes ED, ICU, and IP Non-ICU labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$.

### BUN
```{r BUN p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'}
cp_stratified_data_for_pcharts(defect_data = cp_dashboard_defect_summary, test = "BUN")
```
<h6> Control charts includes ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$.

### HGB
```{r HGB p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'}
cp_stratified_data_for_pcharts(defect_data = cp_dashboard_defect_summary, test = "HGB")
```
<h6> Control charts includes ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$.

### PT
```{r PT p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'}
cp_stratified_data_for_pcharts(defect_data = cp_dashboard_defect_summary, test = "PT")
```
<h6> Control charts includes ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$.

### Rapid Flu
```{r Rapid Flu p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'}
cp_stratified_data_for_pcharts(defect_data = cp_dashboard_defect_summary, test = "Rapid Flu")
# asis_output('<span style = "color: red">test text</span>')
```
<h6> Control charts includes ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$.

### C. diff
```{r C. diff p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'}
cp_stratified_data_for_pcharts(defect_data = cp_dashboard_defect_summary, test = "C. diff")
```
<h6> Control charts includes ED, ICU, and IP Non-ICU labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$.

### All Breast Specimens
```{r All Breast Specimens pchart, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", results='asis'}

ap_stratified_data_for_p_charts(ap_historical_30_day_period_defects, "Breast")

```

### GI Biopsies
```{r GI Biopsies  pchart, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", results='asis'}

ap_stratified_data_for_p_charts(ap_historical_30_day_period_defects, "GI")

```

### Cyto Gyn Specimens
<h1><span style = "color:red">Cyto Gyn Pending - Resolution of Data Issues</h1>
```{r Cyto Gyn Specimens  pchart, eval = FALSE, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", results='asis'}

ap_stratified_data_for_p_charts(ap_historical_30_day_period_defects, "CYTO GYN")


```

### Cyto Non-Gyn Specimens
```{r Cyto Non-Gyn Specimens  pchart, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", results='asis'}

ap_stratified_data_for_p_charts(ap_historical_30_day_period_defects, "CYTO NONGYN")

```


##{-}

## Methodology and Assumptions
### General Notes
The data presented here is based on the compilation of historical data.

### Efficiency Indicator Historical Performance
Turnaround time percentages within target includes labs with valid turnaround times (ie, labs with missing timestamps or negative turnaround times excluded). Resulted volume includes all labs for each site regardless of turnaround time, order priority, or setting to reflect demand on laboratory resources.

All ED and ICU labs are treated as stat, regardless of documented priority. 

**Troponin & Lactate WB:** All labs treated as stat. Settings included in turnaround time analysis are ED, ICU, and Inpatient Non-ICU. All settings included in resulted volume.

**BUN, HGB, & PT:** All labs from ED and ICU are treated as stat; otherwise lab priority is based on documented priority.

**Rapid Flu:** All labs treated as stat. All settings included in resulted volume.

**C. diff:** All labs treated as stat. Turnaround time for ambulatory c. diff labs not tracked but included in total resulted volume. 

**All Breast Specimens:** Included all the primary breast specimens. Only labs from ambulatory and inpatient services included.All settings included in resulted volume.

**GI Biopsies:** Included only the samples that are consisted of GI biopsies. Only primary specimen GI biopsies included. Only labs from ambulatory and inpatient services included. All settings included in resulted volume.

**Cyto Non-Gyn:** Included all the primary Cyto Non-Gyn specimens. Only labs from ambulatory and inpatient services included. All settings included in resulted volume.

### Control Charts of Non-Compliant Labs
These control charts are p-charts used to track non-compliant labs. Non-compliant labs are defined as those labs that do not meet the target turnaround times from receipt in laboratory to result. Only labs with valid turnaround times are included in this analysis. 

Percentage of non-compliant labs calculated as: $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$ 

Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. 

Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$.

**Troponin & Lactate WB:** All labs treated as stat. Settings included in analysis are ED, ICU, and Inpatient Non-ICU.

**BUN, HGB, & PT:** All labs from ED and ICU are treated as stat; otherwise lab priority is based on documented priority.

**Rapid Flu:** All labs treated as stat.

**C. diff:** All labs treated as stat. Turnaround time analysis does not include ambulatory labs.

**All Breast Specimens, GI Biopsies, & Cyto Non-Gyn:** Only labs from ambulatory and inpatient services included in the analysis.












