---
title: "ED Laboratory Efficiency Indicators: 30 Day Lookback"
date: "06/22/2020"
output: html_document
---

<h2><span style="color: red;">Draft - Not for Distribution</span></h2>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r Install and load packages, echo = FALSE, warning = FALSE, message = FALSE}
# install.packages("gridExtra")
# install.packages("scales")

library(timeDate)
library(readxl)
library(bizdays)
library(dplyr)
library(lubridate)
library(reshape2)
library(knitr)
library(kableExtra)
library(formattable)
library(rmarkdown)
library(stringr)
library(writexl)
library(ggplot2)
library(gridExtra)
library(scales)
library(ggQC)
```

```{r Clear history and import relevant data, echo = FALSE, warning = FALSE, message = FALSE}
rm(list = ls())

user_wd <- "J:\\Presidents\\HSPI-PM\\Operations Analytics and Optimization\\Projects\\Service Lines\\Lab KPI\\Data\\SCC Sunquest Script Repo"
user_path <- paste0(user_wd, "\\*.*")
setwd(user_wd)

scc_sun_hist <- read_excel(choose.files(default = user_path, caption = "Select Historical Repository"), sheet = 1, col_names = TRUE)

scc_sun_hist$ResultDate <- as.Date(scc_sun_hist$ResultDate, format = "%m/%d/%y")
lookback_period <- 30
start_date <- max(scc_sun_hist$ResultDate) - (lookback_period - 1)

# Orders for labs, sites, patient setting, and priority
cp_micro_lab_order <- c("Troponin", "Lactate WB", "BUN", "HGB", "PT", "Rapid Flu", "C. diff")
site_order <- c("MSH", "MSQ", "MSBI", "MSB", "MSW", "MSM")
dashboard_pt_setting <- c("ED & ICU", "IP Non-ICU", "Amb")
dashboard_priority_order <- c("All", "Stat", "Routine")

mshs_colors = c("#221f72", "#00AEFF", "#D80B8C", "#7f7f7f")
```

```{r Format historical repository for plotting, echo = FALSE, warning = FALSE, message = FALSE}

# Filter out any non-ED labs and begin summarizing data
dashboard_tat_summary <- scc_sun_hist %>%
  filter(MasterSetting == "ED") %>%
  group_by(Site, ResultDate, Division, Test, 
           DashboardPriority, MasterSetting, 
           ReceiveResultTarget, CollectResultTarget) %>%
  summarize(ResultedVolume = sum(TotalResulted), 
            ResultedVolumeWithTAT = sum(TotalResultedTAT), 
            ReceiveResultInTarget = sum(TotalReceiveResultInTarget), 
            CollectResultInTarget = sum(TotalCollectResultInTarget)) %>%
  mutate(ReceiveResultDefects = ResultedVolumeWithTAT - ReceiveResultInTarget,
         CollectResultDefects = ResultedVolumeWithTAT - CollectResultInTarget,
         ReceiveResultPercent = ReceiveResultInTarget / ResultedVolumeWithTAT,
         CollectResultPercent = CollectResultInTarget / ResultedVolumeWithTAT,
         SafeThreshold = ifelse(Test == "Rapid Flu" | Test == "C. diff", 1.0, 0.95),
         NotSafeThreshold = ifelse(Test == "Rapid Flu" | Test == "C. diff", 0.9, 0.8))

dashboard_vol_summary <- scc_sun_hist %>%
  filter(MasterSetting == "ED") %>%
  group_by(Site, ResultDate, Test, DashboardPriority) %>%
  summarize(ResultedVolume = sum(TotalResulted))

```

```{r Format fields as factors and sort data, echo = FALSE, warning = FALSE, message = FALSE}
# Convert characters to factors
dashboard_tat_summary$Site <- factor(dashboard_tat_summary$Site, levels = site_order)
dashboard_tat_summary$Test <- factor(dashboard_tat_summary$Test, levels = cp_micro_lab_order)
dashboard_tat_summary$DashboardPriority <- factor(dashboard_tat_summary$DashboardPriority, levels = dashboard_priority_order)

# Sort data frame
dashboard_tat_summary <- dashboard_tat_summary %>%
  arrange(Test, Site, DashboardPriority, ResultDate)

```

```{r Custom function for graphing TAT percentage, echo = FALSE, warning = FALSE, message = FALSE}
tat_percentage_graph <- function(data, test_name, site_name, lab_priority, metric) {
  # Subset data for plotting
  tat_data <- data %>%
    filter(ResultDate >= start_date,
           Test == test_name,
           Site == site_name)

  # Store metric name and target turnaround time
  metric_name <- ifelse(metric == "ReceiveResultPercent", "Receive to Result TAT", ifelse(metric == "CollectResultPercent", "Collect to Result TAT", "Error"))
  
  metric_target <- ifelse(metric == "ReceiveResultPercent", unique(tat_data$ReceiveResultTarget), ifelse(metric == "CollectResultPercent", unique(tat_data$CollectResultTarget), "Error"))
  
  ggplot() +
    # Plot safe, at risk, not safe thresholds
    geom_rect(aes(xmin = start_date - 1, xmax = max(tat_data$ResultDate) + 1, ymin = -Inf, ymax = min(tat_data$NotSafeThreshold), fill = "Not Safe", alpha = "Not Safe")) +
    geom_rect(aes(xmin = start_date - 1, xmax = max(tat_data$ResultDate) + 1, ymin = min(tat_data$NotSafeThreshold), ymax = min(data$SafeThreshold), fill = "At Risk", alpha = "At Risk")) +
    geom_rect(aes(xmin = start_date - 1, xmax = max(tat_data$ResultDate) + 1, ymin = min(tat_data$SafeThreshold), ymax = Inf, fill = "Safe", alpha = "Safe")) +
    
    # Plot percentage of labs within TAT target
    geom_point(data = tat_data, aes_string(x = "ResultDate", y = metric), color = mshs_colors[1] , size = 3) +
    geom_line(data = tat_data, aes_string(x = "ResultDate", y = metric), color = mshs_colors[1], linetype = "dashed") +
    
    # Format labels and themes
    labs(title = paste0(test_name, " ", metric_name, ":\n", site_name, " Percentage of ED Labs within Target (",  metric_target, " min)"), x = "Date",  y = "Percentage of Labs", color = "Setting", shape = "Setting") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "right", legend.box = "vertical", legend.title = element_text(size = 10), legend.text = element_text(size = 8),axis.text.x = element_text(angle = 30, hjust = 1)) +
    
    # Format axes
    scale_x_date(limits = c(start_date -1, max(tat_data$ResultDate)+1), breaks = seq(start_date, max(tat_data$ResultDate), by = 3), date_minor_breaks = "1 day", date_labels = "%m/%d/%y", expand = c(0, 0, 0, 0)) +
    scale_fill_manual(name = "Status", values = c("Not Safe" = "red", "At Risk" = "orange", "Safe" = "green"), breaks=c("Not Safe","At Risk","Safe")) +
    scale_alpha_manual(name = "Status", values = c("Not Safe" = 0.15, "At Risk" = 0.15, "Safe" = 0.15), breaks=c("Not Safe","At Risk","Safe")) +
    scale_color_manual(name = "Setting", values = mshs_colors)
}
```

```{r Test TAT percentage graph}
# tat_percentage_graph(data = dashboard_tat_summary, test_name = "BUN", site_name = "MSH",  metric = "ReceiveResultPercent")


```


```{r Custom function for graphing resulted lab volume stratified by order priority, echo = FALSE, warning = FALSE, message = FALSE}

# Function for plotting total resulted lab volume stratified by order priority
resulted_volume_graph <- function(data, test_name, site_name) {
  # Subset data for plotting
  vol_data <- data %>%
    filter(ResultDate >= start_date,
           Test == test_name,
           Site == site_name)

    ggplot() +
    geom_point(data = vol_data, aes(x = ResultDate, y = ResultedVolume), color = mshs_colors[1], size = 3) +
    geom_line(data = vol_data, aes(x = ResultDate, y = ResultedVolume), color = mshs_colors[1], linetype = "dashed") +
    labs(title = paste0(site_name, " ", test_name, " Resulted ED Lab Volume"), x = "Date",  y = "Volume of Labs", color = mshs_colors[1]) +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal", legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8),axis.text.x = element_text(angle = 30, hjust = 1)) +
    scale_x_date(limits = c(start_date -1, max(vol_data$ResultDate)+1), breaks = seq(start_date, max(vol_data$ResultDate), by = 3), date_minor_breaks = "1 day", date_labels = "%m/%d/%y", expand = c(0, 0, 0, 0))
    # scale_y_continuous(sec.axis = sec_axis(~.*1, name = " ", breaks = NULL, label = NULL)) +
    # scale_color_manual(name = "Priority", values = mshs_colors)
}
```

```{r Test volume plot}

# resulted_volume_graph(data = dashboard_vol_summary, test = "BUN", site = "MSQ")

```


```{r Custom function for plotting TAT percentages and resulted volume on single graph, echo = FALSE, warning = FALSE, message = FALSE}

tat_and_volume_plot <- function(data_tat, test_name, site_name, metric) {
  # 
  # Subset turnaround time and volume data based on test, site, and priority
  data_tat_plot <- data_tat %>%
    filter(ResultDate >= start_date & 
             Test == test_name & 
             Site == site_name)

  data_vol_plot <- dashboard_vol_summary %>%
    filter(ResultDate >= start_date & 
             Test == test_name & 
             Site == site_name)
  # 
  # Create printable metric name based on selected metric
  metric_name <- ifelse(metric == "ReceiveResultPercent", "Receive to Result", ifelse(metric == "CollectResultPercent", "Collect to Result", "Error"))
  
  metric_target <- ifelse(metric == "ReceiveResultPercent", unique(data_tat_plot$ReceiveResultTarget), ifelse(metric == "CollectResultPercent", unique(data_tat_plot$CollectResultTarget), "Error"))
  #
  # Determine scale factor for secondary axis based on maximum resulted volume
  base10 <- floor(log10(max(data_vol_plot$ResultedVolume)))
  scale <- ceiling(max(data_vol_plot$ResultedVolume)/(10^(base10-1)))*10^(base10-1)
  #
  # Create plot and standard settings
  ggplot() +
    # Plot safe, at risk, not safe thresholds
    geom_rect(aes(xmin = start_date - 1, xmax = max(data_tat_plot$ResultDate) + 1, 
                  ymin = -Inf, ymax = min(data_tat_plot$NotSafeThreshold), 
                  fill = "Not Safe", alpha = "Not Safe")) +
    geom_rect(aes(xmin = start_date - 1, xmax = max(data_tat_plot$ResultDate) + 1, 
                  ymin = min(data_tat_plot$NotSafeThreshold), ymax = min(data_tat_plot$SafeThreshold), 
                  fill = "At Risk", alpha = "At Risk"), show.legend = FALSE) +
    geom_rect(aes(xmin = start_date - 1, xmax = max(data_tat_plot$ResultDate) + 1, 
                  ymin = min(data_tat_plot$SafeThreshold), ymax = 1, 
                  fill = "Safe", alpha = "Safe"), show.legend = FALSE) + 
    geom_rect(aes(xmin = start_date - 1, xmax = max(data_tat_plot$ResultDate) + 1, 
                  ymin = 1, ymax = Inf, fill = "N/A", 
                  alpha = "N/A"), show.legend = FALSE) +
    
    # Plot percentage of labs within turnaround time target
    geom_point(data = data_tat_plot, aes_string(x = "ResultDate", y = metric, color = "MasterSetting"), size = 3) +
    geom_line(data = data_tat_plot, aes_string(x = "ResultDate", y = metric, color = "MasterSetting"), linetype = "dashed") +
    
    # Plot resulted volume on secondary axis
    geom_point(data = data_vol_plot, aes(x = ResultDate, y = ResultedVolume/scale, size = "Volume"), 
               color = "#959595", shape = 18) +
    geom_line(data = data_vol_plot, aes(x = ResultDate, y = ResultedVolume/scale, linetype = "Volume"), 
              color = "#959595") +
    # Specify graph labels and themes
    labs(title = paste0(site_name, " ", test_name, " ", metric_name, ":\n", "Percentage of ED Labs within Target TAT (",
                        metric_target, " min)"), 
         x = "Date",  y = "Percentage of Labs", color = "Setting", shape = "Setting", 
         fill = "Status", alpha = "Status", linetype = "Resulted Volume", size = "Resulted Volume") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal", 
          legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8),
          axis.text.x = element_text(angle = 30, hjust = 1)) +
    # Specify fills, shapes, and lines mappings and legends
    scale_fill_manual(name = "Status", values = c("Not Safe" = "red", "At Risk" = "orange", "Safe" = "green", "N/A" = "grey"), 
                      breaks=c("Not Safe","At Risk","Safe")) +
    scale_alpha_manual(name = "Status", values = c("Not Safe" = 0.25, "At Risk" = 0.25, "Safe" = 0.25, "N/A" = 0.5), 
                       breaks=c("Not Safe","At Risk","Safe")) +
    scale_color_manual(name = "% within Target", values = mshs_colors, labels = "All ED Labs") +
    scale_size_manual(name = "Resulted Volume", values = 2, labels = "All ED Labs") + 
    scale_linetype_manual(name = "Resulted Volume", values = "dotted", labels = "All ED Labs") +
    
    # Reorder legends
    guides(color = guide_legend(order = 1, nrow = length(unique(data_tat_plot$MasterSetting)), title.vjust = 1), shape = guide_legend(order = 1, nrow = length(unique(data_tat_plot$MasterSetting)), title.vjust = 1), fill = guide_legend(order = 3, nrow = 3, title.vjust = 1), alpha = guide_legend(order = 3, nrow = 3, title.vjust = 1), 
           size = guide_legend(order = 2, title.vjust = 1), linetype = guide_legend(order = 2, title.vjust = 1)) +
    # Specify axis properties
    scale_x_date(limits = c(start_date -1, max(data_tat_plot$ResultDate)+1), 
                 breaks = seq(start_date, max(data_tat_plot$ResultDate), by = 3), date_minor_breaks = "1 day", 
                 date_labels = "%m/%d/%y", expand = c(0, 0, 0, 0)) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(from = 0, to = 1, length.out = 5), expand = c(0, 0, 0.05, 0), labels = percent_format(accuracy = 1), 
                       sec.axis = sec_axis(~.*scale, name = "Volume of Labs"))
}
```

```{r Test combined plotting function}
# tat_and_volume_plot(dashboard_tat_summary, test = "Troponin", site = "MSH", metric = "ReceiveResultPercent")


```


```{r Custom function for stepping through stratified TAT data, echo = FALSE, warning = FALSE, message = FALSE}
stratified_data_for_plots <- function(tat_data, test) {
  test_df <- tat_data %>% 
    filter(Test == test,
           ResultDate >= start_date)
  sites <- unique(test_df$Site)
  for (site in sites) {
    site_df <- test_df %>%
      filter(Site == site)
    # priorities <- unique(site_df$DashboardPriority)
    # for (priority in priorities) {
    #   priority_df <- site_df %>%
    #     filter(DashboardPriority == priority)
      # print(tat_percentage_graph(data = priority_df, test_name = test, site_name = site, lab_priority = priority, metric = "ReceiveResultPercent"))
      # print(tat_percentage_graph(data = priority_df, test_name = test, site_name = site, lab_priority = priority, metric = "CollectResultPercent"))
      print(tat_and_volume_plot(data_tat = site_df, test_name = test, site_name = site,
                                metric = "ReceiveResultPercent"))
      print(tat_and_volume_plot(data_tat = site_df, test_name = test, site_name = site, 
                                metric = "CollectResultPercent"))
      # }
    print(resulted_volume_graph(data = dashboard_vol_summary, test_name = test, site_name = site))
  }
}
```

# {.tabset}

## Efficiency Indicator Historical Performance {.tabset}

### Troponin
```{r Troponin historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
stratified_data_for_plots(tat_data = dashboard_tat_summary, test = "Troponin")
```
<h6> TAT percentages include ED labs with valid turnaround times. Resulted volumes include all resulted labs. </h6>

### Lactate WB
```{r Lactate WB historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
stratified_data_for_plots(tat_data = dashboard_tat_summary, test = "Lactate WB")
```
<h6> TAT percentages include ED labs with valid turnaround times. Resulted volumes include all resulted labs. </h6>

### BUN
```{r BUN historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
stratified_data_for_plots(tat_data = dashboard_tat_summary, test = "BUN")
```
<h6> TAT percentages include ED labs with valid turnaround times. Resulted volumes include all resulted labs. </h6>

### HGB
```{r HGB historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
stratified_data_for_plots(tat_data = dashboard_tat_summary, test = "HGB")
```
<h6> TAT percentages include ED labs with valid turnaround times. Resulted volumes include all resulted labs. </h6>

### PT
```{r PT historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
stratified_data_for_plots(tat_data = dashboard_tat_summary, test = "PT")
```
<h6> TAT percentages include ED labs with valid turnaround times. Resulted volumes include all resulted labs. </h6>

### Rapid Flu
```{r Rapid Flu historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
stratified_data_for_plots(tat_data = dashboard_tat_summary, test = "Rapid Flu")
```
<h6> TAT percentages include ED labs with valid turnaround times. Resulted volumes include all resulted labs. </h6>

### C. diff
```{r C. diff historical data, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center"}
stratified_data_for_plots(tat_data = dashboard_tat_summary, test = "C. diff")
```
<h6> TAT percentages include ED labs with valid turnaround times. Resulted volumes include all resulted labs. </h6>


<!-- ## Control Charts of Non-Compliant Labs {.tabset} -->

<!-- ```{r Summarize data to calculate defects and defect rates, echo = FALSE, warning = FALSE, message = FALSE} -->

<!-- # Summarize data based on site and priority -->
<!-- dashboard_defect_summary <- dashboard_tat_filter %>% -->
<!--   group_by(Site, ResultDate, Division, Test, DashboardPriority) %>% -->
<!--   summarize(ResultedVolume = sum(ResultedVolume),  -->
<!--             ResultedVolumeWithTAT = sum(ResultedVolumeWithTAT), -->
<!--             ReceiveResultInTarget = sum(ReceiveResultInTarget),  -->
<!--             CollectResultInTarget = sum(CollectResultInTarget), -->
<!--             ReceiveResultDefects = ResultedVolumeWithTAT - ReceiveResultInTarget,  -->
<!--             ReceiveResultDefectRate = ReceiveResultDefects / ResultedVolumeWithTAT) -->

<!-- dashboard_defect_summary <- dashboard_defect_summary[!is.na(dashboard_defect_summary$ReceiveResultDefectRate), ] -->
<!-- ``` -->

<!-- ```{r Custom function for p-charts, echo = FALSE, warning = FALSE, message = FALSE} -->

<!-- receive_result_pchart <- function(data_defect, test_name, site_name, lab_priority) { -->
<!--   #  -->
<!--   # Subset turnaround time and volume data based on test, site, and priority -->
<!--   data_defect_plot <- data_defect %>% -->
<!--     filter(ResultDate >= start_date &  -->
<!--              Test == test_name &  -->
<!--              Site == site_name &  -->
<!--              DashboardPriority == lab_priority) -->
<!--   # Calculate center line -->
<!--   center_line <- mean(QC_Lines(data = data_defect_plot$ReceiveResultDefectRate, n = data_defect_plot$ResultedVolumeWithTAT, method = "p")$pBar) -->
<!--   #  -->
<!--   # Create plot and standard settings -->
<!--   ggplot(data = data_defect_plot, aes(x = ResultDate, y = ReceiveResultDefectRate, n = ResultedVolumeWithTAT)) + -->
<!--   # Create point and connecting lines for defect rate data -->
<!--   geom_point(color = mshs_colors[1], shape = 16, size = 3) + -->
<!--   geom_line(color = mshs_colors[1], linetype = "dashed") + -->
<!--   # Add centerline, upper, and lower control limit lines -->
<!--   stat_QC(method = "p", auto.label = T, color.qc_center = "black") + -->
<!--   geom_label(x = max(data_defect_plot$ResultDate)+1, y = center_line, vjust = 1.2, hjust = 1, label = paste("CL:", percent(center_line, accuracy = 0.1))) + -->
<!--   # Specify graph labels and themes -->
<!--   labs(title = paste(site_name, test_name, lab_priority, "Labs:\n", "Control Chart of Non-Compliant Receive to Result TAT"), x = "Date",  y = "Percent Non-Compliant") + -->
<!--   theme_bw() + -->
<!--   theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom", legend.box = "horizontal",  -->
<!--           legend.title = element_text(size = 8, face = "bold"), legend.text = element_text(size = 8), -->
<!--           axis.text.x = element_text(angle = 30, hjust = 1)) + -->
<!--   # Specify axis properties -->
<!--   scale_x_date(limits = c(start_date -1, max(data_defect_plot$ResultDate)+1), breaks = seq(start_date, max(data_defect_plot$ResultDate), by = 3), date_minor_breaks = "1 day", date_labels = "%m/%d/%y", expand = c(0, 0, 0, 0)) + -->
<!--   scale_y_continuous(labels = percent_format(accuracy = 1)) -->
<!-- } -->


<!-- ``` -->

<!-- ```{r Iterate through defect rate data and plot p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'} -->

<!-- stratified_data_for_pcharts <- function(defect_data, test) { -->
<!--   test_df <- defect_data %>% -->
<!--     filter(Test == test &  -->
<!--              ResultDate >= start_date) -->
<!--   sites <- unique(test_df$Site) -->

<!--   for (site in sites) { -->
<!--     # print(site) -->
<!--     # print(test) -->
<!--     site_df <- test_df %>% -->
<!--       filter(Site == site) -->
<!--     priorities <- unique(site_df$DashboardPriority) -->
<!--     for (priority in priorities) { -->
<!--       # print(priority) -->
<!--       priority_df <- site_df %>% -->
<!--         filter(DashboardPriority == priority) -->
<!--       # Determine average resulted volume over last 30 days to see if p-chart is valid -->
<!--       avg_resulted_volume <- mean(priority_df$ResultedVolumeWithTAT[priority_df$ResultDate >= start_date]) -->
<!--       # print(avg_resulted_volume) -->
<!--       if (avg_resulted_volume >= 50) { -->
<!--         print(receive_result_pchart(data_defect = priority_df, test_name = test, site_name = site, lab_priority = priority)) -->
<!--       } else { -->
<!--         cat(paste('\n<center><h3><i>', site, test, priority, "Labs: Insufficient volume for this analysis (n<50).</h3> \n <h4>(Average resulted volume over last 30 days:", round(avg_resulted_volume, digits = 0), "specimens.)", '</i></h4></center>\n\n<br><br>')) -->
<!--       } -->
<!--     } -->
<!--   } -->
<!-- } -->

<!-- ``` -->

<!-- ### Troponin -->
<!-- ```{r Troponin p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'} -->
<!-- stratified_data_for_pcharts(defect_data = dashboard_defect_summary, test = "Troponin") -->
<!-- ``` -->
<!-- <h6> Control charts includes ED, ICU, and IP Non-ICU labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$. -->


<!-- ### Lactate WB -->
<!-- ```{r Lactate WB p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'} -->
<!-- stratified_data_for_pcharts(defect_data = dashboard_defect_summary, test = "Lactate WB") -->
<!-- ``` -->
<!-- <h6> Control charts includes ED, ICU, and IP Non-ICU labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$. -->

<!-- ### BUN -->
<!-- ```{r BUN p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'} -->
<!-- stratified_data_for_pcharts(defect_data = dashboard_defect_summary, test = "BUN") -->
<!-- ``` -->
<!-- <h6> Control charts includes ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$. -->

<!-- ### HGB -->
<!-- ```{r HGB p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'} -->
<!-- stratified_data_for_pcharts(defect_data = dashboard_defect_summary, test = "HGB") -->
<!-- ``` -->
<!-- <h6> Control charts includes ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$. -->

<!-- ### PT -->
<!-- ```{r PT p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'} -->
<!-- stratified_data_for_pcharts(defect_data = dashboard_defect_summary, test = "PT") -->
<!-- ``` -->
<!-- <h6> Control charts includes ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$. -->

<!-- ### Rapid Flu -->
<!-- ```{r Rapid Flu p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'} -->
<!-- stratified_data_for_pcharts(defect_data = dashboard_defect_summary, test = "Rapid Flu") -->
<!-- # asis_output('<span style = "color: red">test text</span>') -->
<!-- ``` -->
<!-- <h6> Control charts includes ED, ICU, IP Non-ICU, and Ambulatory labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$. -->

<!-- ### C. diff -->
<!-- ```{r C. diff p-charts, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 5, fig.width = 8, fig.align="center", eval = TRUE, results = 'asis'} -->
<!-- stratified_data_for_pcharts(defect_data = dashboard_defect_summary, test = "C. diff") -->
<!-- ``` -->
<!-- <h6> Control charts includes ED, ICU, and IP Non-ICU labs with valid turnaround times. Percent non-compliant represents fraction of labs outside target turnaround time and is calculated as $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$. Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$. Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$. -->

##{-}

## Methodology and Assumptions
### General Notes
The data presented here is based on the compilation of historical data.

### Efficiency Indicator Historical Performance
Turnaround time percentages within target includes labs with valid turnaround times (ie, labs with missing timestamps or negative turnaround times excluded). Resulted volume includes all labs for each site regardless of turnaround time, order priority, or setting to reflect demand on laboratory resources.

All ED labs are treated as stat, regardless of documented priority. 

**Troponin & Lactate WB:** All labs treated as stat. Settings included in turnaround time analysis are ED, ICU, and Inpatient Non-ICU. All settings included in resulted volume.

**BUN, HGB, & PT:** All labs from ED and ICU are treated as stat; otherwise lab priority is based on documented priority.

**Rapid Flu:** All labs treated as stat. All settings included in resulted volume.

**C. diff:** All labs treated as stat. Turnaround time for ambulatory c. diff labs not tracked but included in total resulted volume. 


<!-- ### Control Charts of Non-Compliant Labs -->
<!-- These control charts are p-charts used to track non-compliant labs. Non-compliant labs are defined as those labs that do not meet the target turnaround times from receipt in laboratory to result. Only labs with valid turnaround times are included in this analysis.  -->

<!-- Percentage of non-compliant labs calculated as: $\frac{Volume Of Resulted Labs Exceeding Target}{Total Volume Of Resulted Labs}$  -->

<!-- Center line represents process mean and is calculated as $\overline{p} =  \frac{\sum_{} np}{n}$.  -->

<!-- Control limits calculated as $\overline{p} \pm 3\sqrt{\frac{\overline{p}(1-\overline{p})}{n}}$. -->

<!-- **Troponin & Lactate WB:** All labs treated as stat. Settings included in analysis are ED, ICU, and Inpatient Non-ICU. -->

<!-- **BUN, HGB, & PT:** All labs from ED and ICU are treated as stat; otherwise lab priority is based on documented priority. -->

<!-- **Rapid Flu:** All labs treated as stat. -->

<!-- **C. diff:** All labs treated as stat. Turnaround time analysis does not include ambulatory labs. -->

